(tentative) Rotational Spectral Unmixing of Exoplanets

### 2017-02-21 paper/main.tex
figure added
mock lightcurves are added

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \begin{center}
	\includegraphics[width=\hsize]{mockdata_3types_map.pdf}
    \includegraphics[width=\hsize]{mockdata_3types_albd.pdf}
	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc.pdf}
    \end{center}
    \caption{Top: our mock data based on IGBP classification map of the Earth, with 3 surface types (ocean: blue, soil: red, vegetation: green). }
\label{fig:mockdata}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In order to see this more quantitatively, we made a grid on the PC plane  with an interval of 0.2 and considered all combinations of three grid points. 
Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha = 1356{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}. 
%
As expected, we find a relatively definite peak near the point of ocean. 
On the other hand, the peak that corresponds to soil is a blur.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \begin{center}
	\includegraphics[width=\hsize]{mockdata_3types_map.pdf}
    \includegraphics[width=\hsize]{mockdata_3types_albd.pdf}
	\includegraphics[width=\hsize]{mockdata_3types_t360_lc.pdf}
    \end{center}
    \caption{Top: our mock data based on IGBP classification map of the Earth, with 3 surface types (ocean: blue, soil: red, vegetation: green). }
\label{fig:mockdata}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In order to see this more quantitatively, we made a grid on the PC plane  with an interval of 0.2 and considered all combinations of three grid points. 
Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha = 1356{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}. 
%
As expected, we find a relatively definite peak near the point of ocean. 
On the other hand, the peak that corresponds to soil is a blur, and it is almost not constrained.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg.pdf}
    \end{center}
    \caption{correlation length $30^{\circ }$. }
\label{fig:noreg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Additional Constraints}
\label{ss:regularization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
